---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.cap="ggcorrplot: visualize correlation matrix using ggplot2"
)
```
    
    
# ggcorrplot: Visualization of a correlation matrix using ggplot2
    
    
The **ggcorrplot** package can be used to **visualize easily** a **correlation matrix** using **ggplot2**. It provides solution for **reordering** the correlation matrix and displays the **significance level** on the correlogram. It includes also a function for computing a matrix of **correlation p-values**. It's inspired from the package [corrplot](http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram).  
   
   
Find out more at http://www.sthda.com/english/ggcorrplot.
    
   
     
## Installation and loading
    
    
```{r, eval = FALSE}
# Install
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/ggcorrplot")
```

    
```{r}
# Loading
library(ggcorrplot)
```
    
    
## Getting started
     
     
### Compute a correlation matrix
     
The *mtcars* data set will be used in the following R code. The function **cor_pmat()** [in **ggcorrplot**] computes a matrix of correlation p-values. 
     
     
```{r, fig.show = "asis"}
# Compute a correlation matrix
data(mtcars)
corr <- round(cor(mtcars), 1)
corr

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(mtcars)
p.mat
```
    
    
## Correlation matrix visualization
    
    
```{r demo-ggcorrplot, fig.show = "asis", fig.width=5, fig.height=5}
# Visualize the correlation matrix
# --------------------------------
# method = "square" (default)
ggcorrplot(corr)
# method = "circle"
ggcorrplot(corr, method = "circle")

# Reordering the correlation matrix
# --------------------------------
# using hierarchical clustering
ggcorrplot(corr, hc.order = TRUE, outline.col = "white")

# Types of correlogram layout
# --------------------------------
# Get the lower triangle
ggcorrplot(corr, hc.order = TRUE, type = "lower",
     outline.col = "white")
# Get the upeper triangle
ggcorrplot(corr, hc.order = TRUE, type = "upper",
     outline.col = "white")

# Change colors and theme
# --------------------------------
# Argument colors
ggcorrplot(corr, hc.order = TRUE, type = "lower",
   outline.col = "white",
   ggtheme = ggplot2::theme_gray,
   colors = c("#6D9EC1", "white", "#E46726"))

# Add correlation coefficients
# --------------------------------
# argument lab = TRUE
ggcorrplot(corr, hc.order = TRUE, type = "lower",
   lab = TRUE)

# Add correlation significance level
# --------------------------------
# Argument p.mat
# Barring the no significant coefficient
ggcorrplot(corr, hc.order = TRUE,
    type = "lower", p.mat = p.mat)
# Leave blank on no significant coefficient
ggcorrplot(corr, p.mat = p.mat, hc.order = TRUE,
    type = "lower", insig = "blank")
```

     
