---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # out.width = "100%",
  # dpi = 300,
  fig.path = "tools/README-",
  fig.cap = "ggcorrplot: visualize correlation matrix using ggplot2"
)
```
    
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ggcorrplot)](https://cran.r-project.org/package=ggcorrplot)
[![CRAN Checks](https://cranchecks.info/badges/summary/ggcorrplot)](https://cran.r-project.org/web/checks/check_results_ggcorrplot.html)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.2.999-orange.svg?style=flat-square)](https://github.com/kassambara/ggcorrplot)


# ggcorrplot: Visualization of a correlation matrix using ggplot2
    
    
The **ggcorrplot** package can be used to **visualize easily** a **correlation matrix** using **ggplot2**. It provides a solution for **reordering** the correlation matrix and displays the **significance level** on the correlogram. It includes also a function for computing a matrix of **correlation p-values**. 
   
   
Find out more at http://www.sthda.com/english/wiki/ggcorrplot.
    
   
  
## Installation and loading
    
ggcorrplot can be installed from `CRAN` as follow:

```{r, eval = FALSE}
install.packages("ggcorrplot")
```
    
Or, install the latest version from GitHub:

```{r, eval = FALSE}
# Install
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/ggcorrplot")
```

```{r, message = FALSE, warning = FALSE}
# Loading
library(ggcorrplot)
```
    
## Getting started
     
### Compute a correlation matrix
     
The *mtcars* data set will be used in the following R code. The function
**cor_pmat()** [in **ggcorrplot**] computes a matrix of correlation p-values.

```{r, fig.show = "asis"}
# Compute a correlation matrix
data(mtcars)
corr <- round(cor(mtcars), 1)
head(corr[, 1:6])

# Compute a matrix of correlation p-values
p.mat <- cor_pmat(mtcars)
head(p.mat[, 1:4])
```
    
## Correlation matrix visualization
    
```{r demo-ggcorrplot, fig.show = "asis", fig.width=5, fig.height=5}
# Visualize the correlation matrix
# --------------------------------
# method = "square" (default)
ggcorrplot(corr)
# method = "circle"
ggcorrplot(corr, method = "circle")

# Reordering the correlation matrix
# --------------------------------
# using hierarchical clustering
ggcorrplot(corr, hc.order = TRUE, outline.color = "white")

# Types of correlogram layout
# --------------------------------
# Get the lower triangle
ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           outline.color = "white")

# Get the upper triangle
ggcorrplot(corr,
           hc.order = TRUE,
           type = "upper",
           outline.color = "white")

# Change colors and theme
# --------------------------------
# Argument colors
ggcorrplot(
  corr,
  hc.order = TRUE,
  type = "lower",
  outline.color = "white",
  ggtheme = ggplot2::theme_gray,
  colors = c("#6D9EC1", "white", "#E46726")
)

# Add correlation coefficients
# --------------------------------
# argument lab = TRUE
ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           lab = TRUE)

# Add correlation significance level
# --------------------------------
# Argument p.mat
# Barring the no significant coefficient
ggcorrplot(corr,
           hc.order = TRUE,
           type = "lower",
           p.mat = p.mat)

# Leave blank on no significant coefficient
ggcorrplot(
  corr,
  p.mat = p.mat,
  hc.order = TRUE,
  type = "lower",
  insig = "blank"
)
```

