---
title: "Introduction to ggcorrplot"
author: "Alboukadel Kassambara"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    fig_width: 6
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{Introduction to ggcorrplot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  dpi = 200,
  fig.align = "center",
  out.width = "80%"
)
```

**ggcorrplot** draws a correlation matrix as a **ggplot2** plot. Because the
result is an ordinary ggplot object, you keep the full ggplot2 vocabulary:
restyle it with a theme, add layers or annotations, and compose it with other
plots using `+`.

This vignette walks through the package end to end: computing the inputs,
choosing a glyph and layout, reordering by clustering, adding the coefficients,
marking statistical significance, and restyling the result.

```{r}
library(ggcorrplot)
```

# The inputs: a correlation matrix and its p-values

Every plot starts from a correlation matrix. The examples use the built-in
`mtcars` data set.

```{r}
data(mtcars)
corr <- round(cor(mtcars), 1)
corr[1:5, 1:5]
```

To mark significance later, you also need the matrix of correlation p-values.
`cor_pmat()` computes it with `stats::cor.test()`:

```{r}
p.mat <- cor_pmat(mtcars)
p.mat[1:5, 1:5]
```

`ggcorrplot()` never computes correlations itself — it takes a matrix you
already have. That means it works equally well with a partial correlation
matrix, a distance-derived similarity, or any other square matrix in
`[-1, 1]` (and, with `legend.limit = NULL`, matrices outside that range such as
a covariance matrix).

# Basic correlogram

The default encodes each correlation as a colored square. `method = "circle"`
encodes the value with the circle's area instead, which reads well when you want
the magnitude to pop out.

```{r basic, fig.show = "hold", out.width = "48%", fig.align = "default"}
ggcorrplot(corr)
ggcorrplot(corr, method = "circle")
```

When `method = "circle"`, `circle.scale` tunes the circle sizes for your output
device.

```{r circle-scale}
ggcorrplot(corr, method = "circle", circle.scale = 0.6)
```

# Reorder by clustering

Ordering the variables by hierarchical clustering brings correlated variables
next to each other, so the block structure becomes visible. Set
`hc.order = TRUE`; `hc.method` chooses the linkage (as in `hclust()`).

```{r hc}
ggcorrplot(corr, hc.order = TRUE, outline.color = "white")
```

`hc.rect` then draws rectangles around the clusters obtained by cutting the tree
into `k` groups — a quick way to highlight the blocks.

```{r hc-rect}
ggcorrplot(corr, hc.order = TRUE, hc.rect = 3, outline.color = "white")
```

# Layout: triangles and mixed glyphs

For a symmetric matrix the two triangles carry the same information, so you can
show just one with `type = "lower"` or `type = "upper"`.

```{r triangle, fig.show = "hold", out.width = "48%", fig.align = "default"}
ggcorrplot(corr, hc.order = TRUE, type = "lower", outline.color = "white")
ggcorrplot(corr, hc.order = TRUE, type = "upper", outline.color = "white")
```

A **mixed layout** draws a different glyph in each triangle. Set `lower.method`
and/or `upper.method` to `"square"`, `"circle"`, or `"number"`; the variable
names are placed on the diagonal. A common choice is the coefficients as numbers
on one side and circles on the other. Adding `cell.grid = TRUE` boxes every cell
so the glyphs sit in a tidy grid:

```{r mixed, fig.width = 6.5, fig.height = 6}
ggcorrplot(corr,
  lower.method = "number", upper.method = "circle",
  cell.grid = TRUE, show.legend = FALSE
)
```

With `"number"`, the coefficient text is colored on the same scale as the fill,
so values near zero fade out and the strong correlations stand out.

# Add the coefficients

`lab = TRUE` prints the correlation coefficient in each cell. `lab_size`,
`lab_col`, and `lab_fontface` control its appearance.

```{r lab, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr, hc.order = TRUE, type = "lower", lab = TRUE)
```

Two options match common conventions for correlation tables:

- `leading.zero = FALSE` drops the leading zero (`.85` instead of `0.85`).
- `nsmall` keeps a fixed number of decimals (e.g. `nsmall = 2` shows `0.70`).

```{r lab-style, fig.width = 6, fig.height = 5.6}
ggcorrplot(cor(mtcars[, 1:6]),
  lab = TRUE, lab_size = 3.5,
  leading.zero = FALSE, nsmall = 2,
  type = "lower"
)
```

# Mark statistical significance

Supplying `p.mat` lets the plot convey which correlations are significant at
`sig.level` (default `0.05`). There are three styles, chosen with `insig`.

**`insig = "pch"` (default)** crosses out the non-significant cells:

```{r insig-pch, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr, hc.order = TRUE, type = "lower", p.mat = p.mat)
```

**`insig = "blank"`** hides them entirely:

```{r insig-blank, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr, hc.order = TRUE, type = "lower", p.mat = p.mat, insig = "blank")
```

**`insig = "stars"`** flips the emphasis: rather than crossing out the
non-significant cells, it marks the **significant** ones with significance stars
(`***`, `**`, `*` for *p* < 0.001, 0.01, 0.05). With the default `lab = FALSE`
this is a standalone significance map:

```{r insig-stars, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr, p.mat = p.mat, insig = "stars")
```

With `lab = TRUE`, the stars are appended to the coefficients instead
(`-0.85***`), so one plot shows both the value and its significance:

```{r sig-stars, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr,
  type = "lower", p.mat = p.mat,
  lab = TRUE, insig = "stars"
)
```

# Colors and theme

`colors` sets the diverging gradient. A length-3 vector maps to low / mid /
high; any longer vector (for example an 11-color palette) is spread evenly
across the scale.

```{r colors, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr,
  hc.order = TRUE, type = "lower", outline.color = "white",
  colors = c("#6D9EC1", "white", "#E46726")
)
```

`ggtheme` swaps the base ggplot2 theme, and `tl.cex`, `tl.col`, `tl.srt` style
the variable-name labels. `legend.limit` controls the color-scale range — set it
to `NULL` to use the data range, which is what you want for a covariance matrix.

```{r theme, fig.width = 6, fig.height = 5.6}
ggcorrplot(corr,
  hc.order = TRUE, type = "lower",
  ggtheme = ggplot2::theme_minimal,
  tl.col = "gray30", tl.srt = 90,
  colors = c("#003C67", "white", "#8F2727")
)
```

# It is a ggplot: compose freely

Because `ggcorrplot()` returns a ggplot object, you refine it with the usual
ggplot2 grammar — titles, captions, and any additional layer:

```{r compose, fig.width = 6, fig.height = 5.8}
library(ggplot2)

ggcorrplot(corr, hc.order = TRUE, type = "lower", outline.color = "white") +
  labs(
    title = "Correlations among mtcars variables",
    caption = "Hierarchically clustered"
  ) +
  theme(plot.title = element_text(face = "bold"))
```

The fixed 1:1 aspect ratio comes from `coord_fixed()`. To let the cells fill the
plotting area — useful with many long variable names — use `coord.fixed = FALSE`
(or add your own `+ coord_*`, since the last coordinate system wins).

Saving works the same as any ggplot:

```{r save, eval = FALSE}
p <- ggcorrplot(corr, hc.order = TRUE, lab = TRUE)
ggplot2::ggsave("correlogram.png", p, width = 7, height = 6, dpi = 300)
```

# Computing p-values with `cor_pmat()`

`cor_pmat(x, ...)` returns the symmetric matrix of p-values from
`stats::cor.test()`, and passes `...` through to it — so you can, for example,
request a Spearman test:

```{r pmat, eval = FALSE}
cor_pmat(mtcars, method = "spearman")
```

The `use` argument controls how missing values are handled when deciding which
cells are `NA`, mirroring `stats::cor()`: the default
`"pairwise.complete.obs"` tests every pair with enough overlapping observations,
while `"everything"` sets a pair to `NA` as soon as either variable has a missing
value (so its `NA` pattern lines up with `cor(x)`).

# Session information

```{r session}
sessionInfo()
```
